MetaTracts - A Method for Robust Extraction and Visualization of Carbon Fiber Bundles in Fiber Reinforced Composites

### 2014-12-09 chapters/MetaTracts.tex
minor updates
integrated acknowledgements, updated authors list

%
\begin{figure}[tb]
\centering
%\includegraphics[width=0.45\textwidth]{images_pvis/figure3}
%\includegraphics[width=0.5\textwidth,  trim = 0mm 90mm 0mm 0mm, clip]{images_pvis/figure3}
\includegraphics[width=\linewidth]{images_pvis/reliable_hessian.pdf}
 \vspace{-1.5em}
\caption{Reliable Hessians. (a) Colored according to Orientation vector mapped to RGB. (b) 2D slice along Z and (c) along X axis. (d) Magnified region marked in green square.}
\label{fig:reliable_hessian}
\end{figure}

@@

%\acknowledgements{
% The research leading to these results has received funding from the European Union’s Seventh Framework Programme (FP7/2007-2013) under grant agreement ACP2-GA-2012-314562-QUICOM. Our special thanks go to Ilya Ilya Straumit (KU Leuven) who provided us with dataset1.
%}

>>>>

%
\begin{figure}[tb]
\centering
%\includegraphics[width=0.45\textwidth]{images_pvis/figure3}
%\includegraphics[width=0.5\textwidth,  trim = 0mm 90mm 0mm 0mm, clip]{images_pvis/figure3}
\includegraphics[width=\linewidth]{images_pvis/reliable_hessian.pdf}
 \vspace{-1.5em}
\caption{Reliable Hessians. (a) Colored according to Orientation vector mapped to RGB. (b) 2D slice along Z and (c) along X axis. (d) Magnified region marked in white square.}
\label{fig:reliable_hessian}
\end{figure}

@@

\acknowledgements{
The research leading to these results has received funding from the European Union’s Seventh Framework Programme (FP7/2007-2013) under grant agreement ACP2-GA-2012-314562-QUICOM. Our special thanks go to Ilya Ilya Straumit (KU Leuven) who provided us with dataset1.
}
